\documentclass[a4paper, 12pt]{extarticle}
\usepackage{fullpage}
\input{../../preamble.tex}
\renewcommand{\emph}{\textbf}
\begin{document}
 \textbf{ I have chosen this topic because}


brief overview 


wearing a face mask helps prevent 

\emph{However,} there has been less guidance 

U.S. Centers for Disease Control and Prevention  
not  N95  
health care workers 

\emph{However,}cornucopia

Chinese-made KN95s and South Korean–made KF94s

September 10


\emph{In the first part of my talk I would like to consider} 

filtration, fit and comfort. 

Filtration 

For example, an N95 

\emph{However,} that does little good if 
gaps around the mask air 

well-fitted sit snugly  face  chin no gaps around  nose mouth. 

\emph{Also,} comfort 

intolerable

\emph{Now, I’d like to move on to the next part of my presentation, which is about the best masks on the market.}

In the absence which brands  best protection, some skilled amateurs have  stepped in to fill the gap. Aaron Collins mechanical engineer at Seagate Technology

mask-testing setup in bathroom, evaluates masks filtration efficiency by generating aerosols of sodium chloride. \emph{Then} he uses a condensation particle counter --- a device that measures the concentration of particles inside and outside a mask he is wearing --- determine inward leakage through and around the mask. \emph{Also,} Collins tests “pressure drop,”   KN95s  Powecom 

\emph{Despite} N95 standard children, manufacturers . small faces and are easy to put on.  tolerate


\emph{We have come to the final part of my talk about} facial hair, reusing masks and double masking.


\emph{Next}, let's discuss reusing masks. KN95s  considered disposable. \emph{However,} be worn multiple times.
have a few in rotation, reusing one every three days or so, 

And, \emph{finally,} double masking. \emph{Although} the pressure drop was almost twice as high as that of an N95 

\emph{That brings me to the end of my talk. Let me go over the key points again. I have told you} \emph{we have known} \emph{ lastly} we have
discussed 

\emph{To conclude I’d like to leave you with the following thought}.

enough high quality masks for everyone, perhaps  ditch loose-fitting for \emph{Thank you for your attention. If you have any questions, I’ll be happy to answer them. }
\end{document}
