\documentclass[a4paper]{article}
\input{../../preamble.tex}
\title{Oral rendering}
\begin{document}
	\maketitle
\pagenumbering{gobble}
\noindent
The article I’m going to speak about is taken from baronmag.ca. The headline of the article is “7 Reasons Why You Should Invest in Education Today”. The key issue of the article is education as one of the best ways to invest in your future.


The author starts by telling the reader that many people forget about education in the process of looking for better opportunities for financial and other investment.


After that the author provides many reasons why we still should take it into account. Firstly, education makes you a better, more interesting person, and even after graduation there are too many things to learn in the world. Secondly, learning enriches your life, whether it’s learning more about sports, nutrition, global cultures, photography, painting, or yoga. Author then points out that numerous studies have shown that education helps people to avoid demotivation by providing challenges that tests their skills and abilities. Next, whether it’s learning a language or enrolling in a free online course, these activities can benefit your future career by improving your professional profile and thus land you a better paying job. Also, education boosts creativity and innovation because it can expand your knowledge of the world, adding new valuable information to your brain and thus enlarging your perspective of the possible. Moreover, the time you invested in your skills, abilities, and knowledge will never be wasted because of these stick with you forever. Finally, for making a good money investment you must be educated enough to make sure that money will stay in your pockets.


In conclusion the author says that investments are important for your financial well-being, but too many people focus on real-estate, stock bonds, or material things, forgetting that education is the best investment with the best long-term returns.
\end{document}
