\documentclass[a4paper]{article}
\input{../../preamble.tex}
\title{Summary of the article\\``Outside the comfort zone''}
\begin{document}
	\maketitle
\pagenumbering{gobble}
\noindent The headline of the article is “Outside the comfort zone”. The main idea of the article is that leaving your comfort zone can help not only you but also those around you.

At the beginning of the article, the author discusses the concept of ``comfort zone'' in general. This concept characterizes a place or state in which you can be for a long time without thinking about problems or any difficulties in life. On the other hand, staying in your comfort zone for a long time can lead you to a state of boredom and melancholy.

Further, the author analyzes various examples of life situations where people find themselves outside the comfort zone. The conclusion is about the same everywhere: these situations temper you as a person and allow you to gain invaluable experience. After overcoming them, you will be able to solve those tasks that you did not even think about before.

After that, the author finally comes to the question of how overcoming yourself can affect others. We learn about the company called ``Common Purpose'', which allows us to better understand not only our own limitations, but also the limitations and difficulties of others. For example, the company organized a meeting with prison inmates for program participants. Together they discussed the problems and limitations of life behind bars. Such an experience is also a kind of way out of the comfort zone, but completely different, allowing you to learn more not only about yourself, but also about others.

In conclusion, the author quotes the founder of the ``Common Purpose'': ``As professionals we cannot afford to be isolated from fellow decision-makers, and as people, we cannot continue to be insulated from our fellow citizens''.
\end{document}
